treats manual

### 2024-08-28 inst/gitbook/03_make.modifiers.Rmd
book rmd up

---
title: "`make.modifiers`"
author: "Thomas Guillerme (guillert@tcd.ie)"
date: "`r Sys.Date()`"
bibliography: [../references.bib]
output:
  html_document: default
  pdf_document: default
---

>>>>

---
title: "treats manual"
author: "Thomas Guillerme (t.guillerme@sheffield.ac.uk)"
date: "`r Sys.Date()`"
bibliography: [../References.bib]
output:
  html_document: default
  pdf_document: default
---

### 2024-08-28 inst/gitbook/04_make.events.Rmd
book rmd up

---
title: "`make.events`"
author: "Thomas Guillerme (guillert@tcd.ie)"
date: "`r Sys.Date()`"
bibliography: [../references.bib]
output:
  html_document: default
  pdf_document: default
---

>>>>

---
title: "treats manual"
author: "Thomas Guillerme (t.guillerme@sheffield.ac.uk)"
date: "`r Sys.Date()`"
bibliography: [../References.bib]
output:
  html_document: default
  pdf_document: default
---

### 2024-08-28 inst/gitbook/05_other_functionalities.Rmd
book rmd up

---
title: "`other functionalities`"
author: "Thomas Guillerme (guillert@tcd.ie)"
date: "`r Sys.Date()`"
bibliography: [../references.bib]
output:
  html_document: default
  pdf_document: default
---

>>>>

---
title: "treats manual"
author: "Thomas Guillerme (t.guillerme@sheffield.ac.uk)"
date: "`r Sys.Date()`"
bibliography: [../References.bib]
output:
  html_document: default
  pdf_document: default
---

### 2024-08-28 inst/gitbook/07_specific_examples.Rmd
book rmd up

---
title: "treats manual"
author: "Thomas Guillerme (guillert@tcd.ie)"
date: "`r Sys.Date()`"
# bibliography: [../References.bib, ../packages.bib]
output:
  html_document: default
  pdf_document: default
---

>>>>

---
title: "treats manual"
author: "Thomas Guillerme (t.guillerme@sheffield.ac.uk)"
date: "`r Sys.Date()`"
bibliography: [../References.bib]
output:
  html_document: default
  pdf_document: default
---

### 2024-08-28 inst/gitbook/index.Rmd
book rmd up

--- 
title: "treats manual"
author: "Thomas Guillerme (guillert@tcd.ie)"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
output: bookdown::gitbook
documentclass: book
bibliography: [../references.bib]
link-citations: yes
github-repo: TGuillerme/treats
description: "treats R package manual"
---

>>>>

--- 
title: "treats manual"
author: "Thomas Guillerme (t.guillerme@sheffield.ac.uk)"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
output: bookdown::gitbook
documentclass: book
bibliography: [../References.bib]
link-citations: yes
github-repo: TGuillerme/treats
description: "treats R package manual"
---
